Blaming the Typeless: \\ Scalable, Human-Centric Python Localization

### 2018-08-25 paper/main.tex
paper

Drawing inspiration from localization algorithms such as
Nate~\cite{learning-to-blame} and the natural language processing term
frequency vector (or ``bag of words'') model~\cite{FIXME}, we represent
each buggy program as a ``bag of abstracted terms''. A \emph{term} is
either a statement or expression.

@@

We investigate the sensitivity of our algorithm to different categories of
Python errors: is our accuracy sensitive to certain kinds of user defects?
We investigate training and testing Top-1 decision trees on only those
subsets of the dataset corresponding to each of the five most common
uncaught exceptions: \lt{TypeError}, \lt{IndexError}, \lt{AttributeError},
\lt{ValueError}, and \lt{KeyError}. Together, these five exceptions make
up FIXME\% of the errors in our dataset.

As shown in \figref{defect-categories}, these per-defect models have
normalized accuracy between 86\% and 115\% of a comparable model trained on
the dataset as a whole. This shows that our algorithm is robust and able to
give high-accuracy fault localizations on a wide variety of defect types.
Having consistent, rather than defect-type-sensitive, performance is
important for debugging-tool
usability~\cite{orso-parnin,Bessey2010,ayewah10}.

@@

In the programming languages community, a large body of work has focused on
localizing faults and providing better error messages, typically through
the use of type information. SHErrLoc~\cite{SHErrLoc} identifies a set of
incompatible type constraints, then chooses the likely type error using the
Bayesian heuristic that the program is probably mostly correct. We rely on the
complementary heuristic that faults will share characteristics
with previously recorded faults, and apply this heuristic to features beyond
just type information. Mycroft~\cite{MYCROFT-type-errors} modifies existing
type inference algorithms to produce a ``correcting set'' for a program with
a type error. Mycroft assumes that the minimal such set is the most
desirable to the user, and has no way to rank multiple equally
small sets. We instead use machine learning to agree with human judgements.
Nate~\cite{learning-to-blame} uses machine learning on static and contextual
features, including static types, to localize type errors in OCaml
code. We employ a similar approach to localize Python faults, but we use
dynamic features as well as static and contextual ones, we handle a wide
variety of errors beyond type errors, and we evaluate our approach on a set of
programs both more heterogeneous and almost two orders of magnitude larger than
the Nate dataset.

>>>>

Drawing inspiration from localization algorithms such as
Nate~\cite{learning-to-blame} and the natural language processing term
frequency vector (or ``bag of words'') model~\cite{Salton:1986:IMI:576628}, we represent
each buggy program as a ``bag of abstracted terms''. A \emph{term} is
either a statement or expression.

@@

We investigate the sensitivity of our algorithm to different categories of
Python errors: is our accuracy sensitive to certain kinds of user defects?
We investigate training and testing Top-1 decision trees on only those
subsets of the dataset corresponding to each of the five most common
uncaught exceptions: \lt{TypeError}, \lt{IndexError}, \lt{AttributeError},
\lt{ValueError}, and \lt{KeyError}. Together, these five exceptions make
up almost 96\% of the errors in our dataset.

As shown in \figref{defect-categories}, these per-defect models have
normalized accuracy between 86\% and 115\% of a comparable model trained on
the dataset as a whole. This shows that our algorithm is robust and able to
give high-accuracy fault localizations on a variety of defect types.
Having consistent, rather than defect-type-sensitive, performance is
important for debugging-tool
usability~\cite{orso-parnin,Bessey2010,ayewah10}.

@@

In the programming languages community, a large body of work has focused on
localizing faults and providing better error messages, typically through
the use of type information. SHErrLoc~\cite{SHErrLoc} identifies a set of
incompatible type constraints, then chooses the likely type error using the
Bayesian heuristic that the program is probably mostly correct. We rely on the
complementary heuristic that faults will share characteristics
with previously recorded faults, and apply this heuristic to features beyond
just type information. Mycroft~\cite{MYCROFT-type-errors} modifies existing
type inference algorithms to produce a ``correcting set'' for a program with
a type error. Mycroft assumes that the minimal such set is the most
desirable to the user, and has no way to rank multiple equally
small sets. We instead use machine learning to agree with human judgements.
Nate~\cite{learning-to-blame} uses machine learning on static and contextual
features, including static types, to localize type errors in OCaml
code. We employ a similar approach to localize Python faults, but we use
dynamic features as well as static and contextual ones, we handle a
variety of errors beyond type errors, and we evaluate our approach on a set of
programs both more heterogeneous and almost two orders of magnitude larger than
the Nate dataset.
